Arrows for Parallel Computations

### 2017-10-25 paper/content/benchmarks.tex
more clarification for the benchmarks

Next is the \torustest benchmark. The results of the comparison of vanilla Eden to our PArrows-based version can be found in Fig.~\ref{fig:torusBenchmark}. While we do not see too much speedup for more than 16 cores, we can prove that the difference between the Eden and PArrows version are again marginal. %The difference between PArrows and Eden is only significant for 16 and 64 cores where it ran 1.7\% and 2.7\% slower which corresponds to a real-time difference of 0.12s and 0.13s. For 256 cores PArrows performed 0.2\% slower which corresponds to 0.01s overhead.

@@

In our distributed memory tests on the full grid we were unable to detect any performance deficiencies of PArrows \wrt Eden that were above of the error margin.
In our distributed memory tests on the full grid the difference between PArrows and Eden was always below the error margin if PArrows performed worse. Even the biggest difference of 12.27\% in the \jacobitest for input $2^{4253}-1$ and 128 cores remained in line with these findings.

>>>>

Next is the \torustest benchmark. The results of the comparison of vanilla Eden to our PArrows-based version can be found in Fig.~\ref{fig:torusBenchmark}. We see that the benchmark scales quite well with more cores until 64 cores. For $>=96$ cores, we still have considerable speedup, but with less slope. We also prove that the difference between the Eden and PArrows version are only marginal with PArrows only being a maximum of $1.7\%$ slower -- for 160 cores -- when outside of the error bar.  %The difference between PArrows and Eden is only significant for 16 and 64 cores where it ran 1.7\% and 2.7\% slower which corresponds to a real-time difference of 0.12s and 0.13s. For 256 cores PArrows performed 0.2\% slower which corresponds to 0.01s overhead.

@@

In the shared memory setting we naturally find that the backends perform differently. Furthermore, in our distributed memory tests on the full grid the difference between PArrows and Eden was almost always below the error margin if PArrows performed worse. Even the biggest difference of 12.27\% in the \jacobitest for input $2^{4253}-1$ and 128 cores remained in line with these findings. The only exception to this was the \torustest, which showed only a $1.7\%$ difference in favour of Eden which is only a marginal slowdown in our opinion.

### 2017-10-25 paper/content/conclusion.tex
spellchecked
more clarification for the benchmarks

\section{Conclusion}
\label{sec:conclusion}
Arrows are a generic concept that allows for powerful composition
combinators. To our knowledge we are first to represent
\emph{parallel} computation with Arrows.
% \olcomment{that strange arrows-based robot interaction paper from 1993 or so! clearly discuss in related work} \done
%
Arrows turn out to be a useful tool for composing parallel
programs. We do not have to introduce new monadic types that wrap the
computation. Instead, we use Arrows in the same manner one uses sequential pure functions. 
%
This work features multiple parallel backends: the already available parallel Haskell flavours. Parallel Arrows, as presented here, feature an implementation of the |ArrowParallel| typeclass for GpH Haskell, |Par| Monad, and Eden. With our approach parallel programs can be ported across these flavours with little to no effort. It is quite straightforward to add further backends. 
%
%
Performance-wise, Parallel Arrows are on par with existing parallel Haskells, as they do not introduce any notable overhead.
%
The benefit is, however, the greatly increased portability of parallel programs.

>>>>

\section{Conclusion}
\label{sec:conclusion}
Arrows are a generic concept that allows for powerful composition
combinators. To our knowledge we are first to represent
\emph{parallel} computation with Arrows.
% \olcomment{that strange arrows-based robot interaction paper from 1993 or so! clearly discuss in related work} \done
%
Arrows turn out to be a useful tool for composing parallel
programs. We do not have to introduce new monadic types that wrap the
computation. Instead, we use Arrows in the same manner one uses sequential pure functions. 
%
This work features multiple parallel backends: the already available parallel Haskell flavours. Parallel Arrows, as presented here, feature an implementation of the |ArrowParallel| type class for GpH Haskell, |Par| Monad, and Eden. With our approach parallel programs can be ported across these flavours with little to no effort. It is quite straightforward to add further backends. 
%
%
Performance-wise, Parallel Arrows are on par with existing parallel Haskells, as they do not introduce any notable overhead in our benchmarks.
%
The benefit is, however, the greatly increased portability of parallel programs.
